\chapter{Used technologies}

\section{Programming languages}
\subsection{Python}
Python is an interpreted, interactive, object-oriented programming language. It
incorporates modules, exceptions, dynamic typing, very high level dynamic data
types, and classes. Python combines remarkable power with very clear syntax. It
has interfaces to many system calls and libraries, as well as to various window
systems, and is extensible in C or C++. It is also usable as an extension
language for applications that need a programmable interface. Finally, Python is
portable: it runs on many Unix variants, on the Mac, and on PCs under MS-DOS,
Windows, Windows NT, and OS/2.

Python is a high-level general-purpose programming language that can be applied
to many different classes of problems. The language comes with a large standard
library that covers areas such as string processing (regular expressions,
Unicode, calculating differences between files), Internet protocols (HTTP, FTP,
SMTP, XML-RPC, POP, IMAP, CGI programming), software engineering (unit testing,
logging, profiling, parsing Python code), and operating system interfaces
(system calls, filesystems, TCP/IP sockets). Look at the table of contents for
The Python Standard Library to get an idea of what’s available. A wide variety
of third-party extensions are also available.
TODO(Add link Python https://docs.python.org/2/faq/general.html)

\subsection{Javascript}
JavaScript (shortened to JS) is an interpreted, object-oriented, weakly typed,
programming language with first-class functions most known as scripting language
for Web pages. It was originally implemented so that client-side scripts could
interact with the user, control the browser, communicate asynchronously and
alter the web page content that was displayed, and now it has evaluated to
involve game  development and applications creation. JavaScript's main purpose
was the creation and embedding of scripts in the HTML client side in order to
guarantee more interactivity with the user. It was created to offer dynamic
tasks such as the transformation of the page elements, visual effects and
immediate reactions to the user actions. But now JS for server-side web is
gaining popularity with the appearance of JavaScript frameworks for that
purpose. 
JavaScript was a purely interpreted language. This means that scripts execute
without preliminary compilation (without conversion of the script text into
machine code). The user's browser interprets the script, that is, analyzes and
immediately executes it. In modern implemented, The user's browser interprets
the script, that is, analyzes and immediatley 
TODO(Add link Mozilla developer network, https://developer.mozilla.org/en-us/docs/web/javascript)

\section{Frameworks}
\subsection{Pyramid}
Pyramid is a fast and low-level Python web framework. It is developed as
part of the Pylons Projects. Even Pyramid isn't famous like Flask and Django, it
minimal, unobtrusive and agnostic design helps in developing more robust and
fast web applications. TODO(Complete) 

\subsection{ReactJS}
React is an open-source front end library developed by Facebook. It's used for
handling view layer for web and mobile apps. ReactJS allows us to create large
web applications that use data which can change over time, without reloading the
page, using reusable UI components. Its main goal is to be fast, simple and
scalable. It is currently one of the most popular JavaScript libraries and it
has strong foundation and large community behind it. React components are
typically written in JSX, a JavaScript extension syntax allowing quoting of HTML
and using HTML tag syntax to render subcomponents.

\subsubsection{Grommet}
Grommet is a UX framework for enterprise applications developed by HP, on top of
ReactJS. It was created to align the desing and developer workflow into one
seamless experience. The Grommet components library is designed to be perfect
complement to the design system. With little setup, developer will be able to
create a Grommet application from scratch in minutes and take the pain out of
translating desing files into unning application code.

\section{Tools and services}
\subsection{AWS}
Amazon Web Services (AWS) is a subsidiary of Amazon.com that provides on-demand
cloud computing platforms. These services operate from many global geographical
regions including 6 in North America. They include Amazon Elastic Compute
Cloud, also known as "EC2", and Amazon Simple Storage Service, also known as
"S3". As of 2016, AWS has more than 70 services, spanning a wide range,
including compute, storage, networking, database, analytics, application
services, deployment, management, mobile, developer tools and tools for the
Internet of Things. Amazon markets AWS as a service to provide large computing
capacity quicker and cheaper than a client company building an actual physical
server farm.

\subsection{Nix}

Nix is a purely functional package manager. This means that it treats packages
like values in purely functional programming languages such as Haskell — they
are built by functions that don’t have side-effects, and they never change after
they have been built. Nix stores packages in the Nix store, usually the
directory /nix/store, where each package has its own unique subdirectory such as

\colorbox{Gray}{\lstinline{nix/store/b6gvzjyb2pg0kjfwrjmg1vfhh54ad73z-firefox-33.1/}}

Where \colorbox{Gray}{\lstinline{b6gvzjyb2pg0...}} is a unique identifier for the package that captures all its
dependencies (it’s a cryptographic hash of the package’s build dependency
graph). This enables many powerful features.

Nix was created by Eelco Dolstra as he's PHD. Eelco is, along with other main
contributors to the Nix ecosystem, a Predictix employment.
\subsection{Nix language}
The Nix expression language is a pure, lazy, functional language. Purity means
that operations in the language don't have side-effects (for instance, there is
no variable assignment). Laziness means that arguments to functions are
evaluated only when they are needed. Functional means that functions are
“normal” values that can be passed around and manipulated in interesting ways.
The language is not a full-featured, general purpose language. Its main job is
to describe packages, compositions of packages, and the variability within
packages.

\subsubsection{NixOS}
Nixos is Linux distribution built on top of the Nix package manager. It
uses the Nix language for declarative configuration which allows realiable
system upgrades.
Although NixOS started as a research project, it is a fully functional and
usable operating system.

\subsubsection{NixOps}
NixOps is a tool for deploying sets of NixOS Linux Machines, either to real
hardware or to virtual machines. It extends NixOS's declarative approach to
system configuration to networks and adds provisioning.

\par
The NixOps Dashboard is a built-in house extension to NixOps and offers the same
content and functionality via a Web UI and a rich RESTful API. Core features
are:

\begin{itemize}
\item User-friendly web-based interface
\item Improved security
\item Scheduled operations (deployments, backups, ...etc)
\item Permanent traceability
\item Clear audit trail
\item Role based access
\end{itemize}

We will be using NixOps Dashboard API to provision servers and deploy the
applications in the cloud in order to benchmark them in a production-like
systems.
