\chapter{Overview}

\section{Introduction}
This introductory chapter presents the general context of the project and gives
an overview of its scope. In the first section, we will specify pedagogical and
professional frame of the project, where we will introduce the host company, its
business field  and the Technical Infrastructure team. Then, in the second
section, we will present some general concepts of the project. Finally, we will
define the project problematic and present the project goals.


\subsection{General context}
In the part we will put the project in its frames, both scholar and
professional. First we will set the pedagogical. Then we will define the
professional frame, i.e Predictix and more specifically the Technical
Infrastructure team.

\subsubsection{Pedagogical Frame}
This project was elaborated in the context of a graduation internship, a final
step of obtaining the National Diploma of computer engineering from the Faculty
of Science of Tunis
The internship was undertook on period of four months, from February 1st to
May 31th, 2017, during which, we integrated the Technical Infrastructure team at
Predictix Tunisia.
\subsubsection{Professional frame}
Predictix is an American company headquartered in Atlanta, GA, USA, with a
center of operations in Tunisia.

Predictix is a fast growing consulting and software company founded in 2005,
headquartered in Atlanta, Georgia USA with affiliations in Tunis, Tunisia,
London, UK and Amsterdam, Netherlands. It merged with LogicBlox in January 2014
which private company that provide the next generation of smart database. This
new database permits to present finished products to the clients in the simplest
ways, after performing a lot of complicated cloud and multicore computing.

Predictix is specialized in providing software solutions implementing predictive
analytic technologies to solve retail problems and improves retailers'
profitability. In fact, it helps Tier 1 TODO retailers and brands make better
merchandising decisions  by eliminating the traditional silos between varrious
buying and selling decision, delivering solutions that evolve easily to adapt to
their ever-changing business and simplifying the process and lowering the stakes
of investing in technology.

As recognition, Gartner, the world's leading information technology research and
advisory company, has classified as a leader, in the Magic Quadrant for
Merchandise Assortment Management Applications in July 2015.

As a matter fact, because of the leading role of Predictix in Cloud based
solutions for retailers. It get acquired by Infor, in 2016.

\subsubsection{Infor}
Infor is the third-largest provider of enterprise applications and services
behind Oracle and SAP. Think: over 70,000 customers in 194 countries for its
industry-specific applications and suites designed for the cloud, on-premises,
or both, that brings in about \$2.5 billion in revenue. To handle this massive
operation, Infor employs 13,000 people across the globe.

Predictix joined Infor as the base of Infor-retail the Infor devision fore
retailers.

Infor on Predictix:
"Atlanta-based Predictix experienced more than 40 percent growth in SaaS
subscriptions in 2015 and counts 5 of the top 15 global retailers as customers,
managing more than \$60bn in weekly forecasts. The company has an engineering-
and science-driven culture with deep expertise in retail and a drive to
revolutionize the industry. LogicBlox, the company's technology platform
underlying all Predictix applications, revolutionizes the development of
next-generation predictive and prescriptive applications, and has attracted
funding from DARPA, the Defense Advanced Research Projects Agency."

Predictix is providing SaaS applications to big retailers, among which the
largest drug retail chain in the United States in sales and profits with annual
sales of over US \$76 billion in 2015, employs over 240,000 people, with more
than 8,000 stores  across all 50 U.S States, the District of Columbia, Puerto
Rico and the US Virgin Islands. As a matter of act, for forecasting purposes,
this client benefited from \$125M from inventory reduction alone, with 20\% of
ongoing. Some of Predictix clients, whose solutions are already on production,
are
\begin{itemize}
\item{Kiabi}
\item{The Home Depot}
\item{Crate and Barrel}
\item{M.Video}
\item{Target}
\end{itemize}

Predictix offers its clients a variety of solutions. The figure gives an
overview of Predictix business units:

TODO

Pricing and Promotions: Retailers, wholesalers and some manufacturers use
Predictix services to help them manage their promotions, pricing and markdowns
for higher profit bottom lines,by offering a very high flexible and
configurable solution that facilitates the user interaction with the results he
gets.

Forecasting  and Replenishment: The firm provides forecasts and replenishment
strategies that enable a retailer to implement the promotional, pricing and
assortment strategies established. Additional profit can be gained by minimizing
inventory levels and reducing lost sales.

Assortment and Space Optimization: Predictix helps retailers to define the
optimal localized assortment for every store and every space. Retailers can
expect category margins to improve 100 basis points or more, and to drive higher
sales, from optimizing their assortment with Predictix ASO.

Planning and  Allocation: Business Consulting at Predictix helps retailers
review their current planning and allocation process and design  new ones for
the future.

In order to provide these solutions , Predictix has forged a number of
strategic partnerships with other companies. Some of which are the following
companies:

LogicBlox: The platform provider for Predictix' solutions. Predictix used
LogicBlox' scalable and declarative database system, programming language and
different environment tools to design and build  its systems. After a
partnership lasting for years, the two companies have merged together.

Amazon Web Services: AWS is a world leader in cloud computing solutions.
Predictix is using AWS' IaaS and PaaS solutions to host its different systems.
The need for cloud

During its life cycle, every client's product goes through a number of steps,
from development to testing to deployment. 

Technical Infrastructure team:

The technical infrastructure team is needed in every step of the client's
product life cycle. Inf  fact, they gather and collect the data, store it, do
batch processing or real-time processing on it, and serve it via an API to a data
scientist who can easily query it. They have extensive knowledge on databases
and best engineering practices. These include handling and logging errors,
monitoring the system, building human-fault-tolerant pipelines, understanding
what is necessary to scale up, addressing continuous integration, knowledge of
database administration, maintaining data cleaning and ensuring a deterministic
pipeline.

The main activities of Predictix' architecture and integration team can be
summarized to:

They intervene, in the beginning of the project when the requirements are
defined. They play the role of consultant as they are consulted to discuss the
data specification, in collaboration with the data science team, with the
client. In fact, their role, at this step is to take all necessary measures in
order to make sure that the data is normalized and consistent.

They intervene, also, in the development of the applications, as they are in
charge of the applications architecture design. In fact, they translate complex
functional and technical requirements into detailed architecture, design and
high performing software with the ability to architect highly scalable
distributed systems.

They are, also, in charge of batch implementation thorough data modelling, rules
definitions, protocol buffers services, etc.

Finally they are responsible of the application being automatically build and
deployed on the cloud, with extremely high attention to the application
performance, as it world affect the application cost.

Tooling:
One of the main duties of the Technical Infrastructure team. Is to create
internal tools that facilitate the development of project, deploying and
monitoring performance and cost.

lb-job-cost: It's a tool for monitoring lb jobs cost of each client's account.
It will give the current actual cost for the month along with the projected cost
for the whole month.

Ops-console: It's a web application that helps engineers at Predictix to monitor
the batch process in real-time.

Command-history: A web applications that monitor the commands used in all
Predictix EC2 machines. It give the user the ability to search for command
usage, for certain user.

Nixops-dashboard:
SaaS solution that allows users with no technical knowledge, to easily provision
Predictix applications on the cloud.  Business consultants, testers, and others are
now able to deploy complex infrastructures with a click of button.


\subsection{General concepts}

In this section, we will be defining the general concepts that the Technical
Infrastructure team work around, and more specifically those that this project
evolves around. We will also clarify the use cases for these technologies and
concepts in Predictix.

\subsubsection{Declarative programming}
Definition:
Declarative programming is a programming paradigm where the developer write code
in such a way that it describes the logic of computation, without describing its
workflow.

\subsubsection{REST architecture}
Rest stands fore REpresntational State Transfer. It is an architecture style for
designing networked applications. It permits creating, modifying resources
easily. Indeed REST is a lightweight alternative to complex mechanism like RPC,
CORBA and SOAP. 

Rest is not a 'standard'. In fact,  it is a guideline to build an efficient
framework for communication between two machines using HTTP protocol. The World
Wide Web itself, based on HTTP, can be viewed as a REST-based architecture. REST
relies on a stateless, client-server, cacheable communication protocol. It is
simple to implement and maintain. In addition, it allows applications to be scalable
by supporting multiple backend services at the same time.

Much like Web Services, a REST service is platform-independent,
language-independent standard-based asit runs on top of HTTP, and is easily used
in the presence of firewalls.

However, there are a few major concepts which make REST unnique from other web
services. In fact , its main key principales are the following:

Unique URL-Resource mapping: Every resouce is mapped to a unique URL. That
refers to a some logical way  to access information. 

Statelessness: All information required to precess the request by server is
contained along with the request. This means that no informatio of the previes
request is maintained by the server. This is inherited from the fact that REST
is based on HTTP.

Action Verbs: REST architecture use HTTP verbs to identify the apropriate
action. The main HTTP verbs used in a REST architecture are GET, POST, PUT and
DELETE. In fact, GET is used by the client to access the resource on the server,
PUT to update a resource, POST to create a new one and DELETE to remove
resource.

Data Exchange formats: REST architecture does not require any particular
encoding for the resource body. JSON and XML are the most used format, but it
can be PROTOBUF, YAML etc. 
