\chapter{Requirement definitions}

\section*{Introduction}

After imbibing the general context of the project, we are going to focus in
the is chapter on providing a full description of out project, that we will be
calling Benchmarks Dashboard. To do so, we will start by analyzing the
requirements and extracting the  functional and non-functional specifications.
Then we will define the Product backlog of the project to achieve. Finally we
will present the general use cases of the project.

\section{Requirements analysis}

\subsection{Design session}
After  the beginning of the internship, we had a on-month training where we were
trained about the different technologies that Predictix is using, such as
LogiQL, Nix and LB. Also, as interns, we had the opportunity, first, to get
familiar with the company's working environment, second, understand better the
project's goal and its added value to its users, and third, were able to collect
the functional and non functional requirements of the project.


\subsection{Functional requirements}
The  purpose of this project is to automate the benchmarking process of the
applications developed in Predictix. For that ther are two main requirements
that need to be addressed.

\subsubsection{Automating "benchmark runs"}
The application should give the ability to the clients, the developers, to run
benchmark with the click of a button. The applicatin must run all the repeated
process without user's interactions. For that 3 operations must be automated:

$\bullet$ \textbf{Deploy the application}: The applications developed in house are SaaS
applicatons, thus they must be deployed to the cloud. The user
choose what the application that want to run benchmark for. Then we need to
automaticly provison a server in the cloud, install the application on that
server along with all dependcies that are needed to run the benchmark.

$\bullet$ \textbf{Load test data}: To have a real and consice measure of the perfoarance of the
application, a data sample should be loaded into the database. This sample should
be the same across all benchmarks runs so it can make sense to compare them. The
data should be loaded as soon as the application is installed.

$\bullet$ \textbf{Run The benchmark}: After loading test data we will run a series of service test
and measure the time each service took to complete the request. Each service
test will be run 3 times to unveil any issues with database warmup.

Finally after the benchmarks completed the result of the test should be stored
for the developer to check and the instance should be unprovisioned.

\subsubsection{Visualize the previous benchmarks}
They developer should be able to see and investigate the result of the
benchmarks. He must be also be able to:

$\bullet$ \textbf{Compare benchmarks}: In this case the user can see differnece
in the overall perfoaramance of the application, between two different dates.

$\bullet$ \textbf{Test history}: The user can see the test history. Thus the
state of the test between all benchmarks, or specifly between two bencharmks.

$\bullet$ \textbf{Benchmark status}: The user can see the status of the
benchmark. Whether they competed successfully or not or they still running. Also
they can see who started the benchmark run, and when he started it.

\section{Product Backlog}
From the previous requirements and some other realted to user mangment we can
extract this table below
\begin{center}
  \begin{tabular}{ | p{1cm}  | p{9cm}  | p{2cm} | p{2cm}| }
    \hline

    ID & User Story                                                                                                        & Priority        & Estimation\\ \hline

    1 & As a user, I want to login using my username and password and start using the application right away.              & 2              & 99        \\ \hline
    2 & As a user, I want to visualize account’s applications and select one to run new benchmark                          & 1              & 99        \\ \hline
    3 & As a user, I want to visualize the list of accounts.                                                               & 4              & 99        \\ \hline
    4 & As a user, I want to visualize the status of account’s benchmarks.                                                 & 6              & 99        \\ \hline
    6 & As a user, I want to be able to choose an account and visualize it’s history                                       & 5              & 99        \\ \hline
    7 & As a user, I want to be able to choose a benchmark and visualize the tests durations.                              & 6              & 99        \\ \hline
    8 & As a user, I want to be able to choose a test in an account and visualize the history over all benchmarks.         & 9              & 99        \\ \hline
    9 & As an account administrator, I want to be able to grant ‘Run benchmark’  right to users also be able to revoke it. & 9              & 99        \\ \hline
    10 & As an administrator, I want to be able to manage all accounts.                                                    & 3              & 99        \\ \hline

    \hline
  \end{tabular}
\end{center}
